%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.3 (22/9/2018)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% v1.3 author:
% Zachary Taylor
%
% v1.3 repository:
% https://github.com/ZDTaylor/Deedy-Resume-Reversed
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Add various styling and section options and allow for multiple pages smoothly.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.3:
% 1. Removed MacFonts version as I have no desire to maintain it nor access to macOS
% 2. Switched column ordering
% 3. Changed font styles/colors for easier human readability
% 4. Added, removed, and rearranged sections to reflect my own experience
% 5. Hid last updated
%
% v1.2:
% 1. Added publications in place of societies.
% 2. Collapsed a portion of education.
% 3. Fixed a bug with alignment of overflowing long last updated dates on the top right.
%
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-reversed}


\pagestyle{fancy}
\fancyhf{}

% Place Page X of Y on the right-hand
% side of the footer
\fancyfoot[R]{Page \thepage \hspace{1pt} of \pageref{LastPage} }

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Luis Miguel Rojas Aguilera}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
 \href{https://github.com/roj4s}{github.com/roj4s} | \href{mailto:rojas.luis.mail@gmail.com}{rojas.luis.mail@gmail.com} | \href{tel:+5592982114961}{+55 (92) 982114961}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.6\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{StackSpotAI (ai.stackspot.com)}
\descript{| Full-Stack Engineer }
\location{Apr 2024 – Currently}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed a AI Developer assistant using Retrieval Augmentation (Langchain, PGVector, PymuPDF), LLMs and Embeddings models (OpenAI).
\item REST APIs using FastApi, sqlAlchemy, Redis.
\item Services orchestration and deploy with Docker, Github Actions and Terraform.
\item Monitoring and observability with Datadog, Graphana, Metabase Cloudwatch and Langsmith.
\item Cloud-based solutions using Kafka (AWS MSK), SNS, Lambda functions, APIGateway, DynamoDB, CloudFormation, CDK.
\item Front-end UI components with React, react-redux, react-router, MUI.
\item Unit\&Integration tests with pytest, jest and cypress.
\item BFF services using AWS lambda functions, APIGateway and DynamoDB.
\end{tightemize}
\sectionsep

\runsubsection{Vortigo (platform.vease.ai)}
\descript{| FullStack Engineer }
\location{Apr 2024 – Nov 2024}
\begin{tightemize}
\item RAG-based Chatbot from PDF documents (OpenAI, Bedrock, PGVector, Langchain, PymuPDF).
\item REST APIs using FastApi, pymongo, Redis.
\item Front-end with NextJS, shadcn, tailwind.
\item AWS Lambda functions for embedding indexing from PDF documents integrated with SNS and S3. 
\item Services orchestration and deploy with Docker, EKS and Azure pipelines.
\end{tightemize}
\sectionsep

\runsubsection{FTLNetworkX}
\descript{| Python Developer }
\location{May 2024 – Jul 2024}
\begin{tightemize}
\item Platform for in-house router's appliances network data analysis.
\item Implemented services to collect network data from OpenSense API on FreeBSD and store to ClickHouse database and Graphana, using FastApi.
\item Create Graphana dashboards with aggregations on top of ClickHouse records.
\end{tightemize}
\sectionsep

\runsubsection{Magic Payments (magic-21.mintlify.app)}
\descript{| FullStack Web Developer }
\location{Aug 2023 – May 2024}
\begin{tightemize}
\item Payment gateway for transactions between bank checking accounts.
\item Full-Stack Web development with Django, NextJs, shadcn and TailwindCss
\item REST APIs with Django Rest Framework.
\item Webhooks integrations with Dwolla and Plaid for banking operations.
\item CI/CD pipelines with Docker and Github actions.
\item Unit tests with pytest and jest.
\end{tightemize}
\sectionsep

\runsubsection{Underwriter Labs (ul.com)}
\descript{| FullStack Web Developer }
\location{March 2023 – Aug 2023}
\begin{tightemize}
\item Full-Stack Web development with NodeJs, Vue (vuetify), Quasar and TailwindCss.
\item Vue.js to develop dynamic and interactive user interfaces.
\item Configuration of auto-scaling groups, load balancers and AWS services like EC2, S3, RDS, and Lambda functions.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\fontsize{8pt}{10pt}\selectfont
\section{\fontsize{12}{15}\selectfont Education}

\subsection{\fontsize{10}{12}\selectfont Master's Degree in Computer Sciences}
\descript{\fontsize{8}{10}\selectfont Universidade Federal do Amazonas, Brasil (UFAM ufam.edu.br)}
\location{\fontsize{8}{10}\selectfont March 2015 - March 2017}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Nanodegree Machine Learning Engineer}
\descript{\fontsize{8}{10}\selectfont Udacity}
\location{\fontsize{8}{10}\selectfont Jan 2019 - Jan 2020}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Bachelor's Degree in Informatics}
\descript{\fontsize{8}{10}\selectfont UCI (Havana, Cuba)}
\location{\fontsize{8}{10}\selectfont Jan 2010 - Feb 2014}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\fontsize{12}{15}\selectfont Skills}
\subsection{\fontsize{10}{12}\selectfont Programming}
\location{9+ years:}
Python \textbullet{} JavaScript \textbullet{} Bash \\
\location{5+ years:}
C++ \textbullet{} PHP \textbullet{} TypeScript \textbullet{} LaTeX\\
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Technology}
Git/Github \textbullet{} AWS \textbullet{} Linux \\
React \textbullet{} NextJs \textbullet{} Angular \textbullet{} Vue \textbullet{} ExtJs\\
Django \textbullet{} FastApi \textbullet{} Flask \textbullet{}  Tornado \\
EKS \textbullet{} CloudWatch \textbullet{} Lambda \textbullet{} DynamoDb \textbullet{} APIGateway \textbullet{} SNS  \textbullet{} SQS \textbullet{} SAM \textbullet{} Localstack \textbullet{} MKS \textbullet{} RabbitMQ \textbullet{} CloudFormation \textbullet{} CDK\\
Cypress \textbullet{} Jest \textbullet{} Pytest\\
Yii \textbullet{} Symfony\\
MLFlow \textbullet{} Keras \textbullet{} Tensorflow \textbullet{} pandas \textbullet{} numpy\\
Docker \textbullet{} Kubernetes \textbullet{} Github Actions \textbullet{} CircleCI \textbullet{} Terraform\\
Datadog \textbullet{} Graphana \textbullet{} Metabase \textbullet{} ElasticStack\\
MongoDb \textbullet{} Postgres \textbullet{} MySQL \textbullet{} Clickhouse \textbullet{} DyamoDB \textbullet{} Redis\\
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Management}
Jira \textbullet{} Confluence \textbullet{} Trello \\
Scrum \textbullet{} Kanban \textbullet{} RUP \textbullet{} Xtreme Programming \\
Loom \textbullet{} Notion \textbullet{} Signal\\
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Languages}
English \textbullet{} TOEFL C2 \textbullet{} Advanced\\
Spanish \textbullet{} Native\\
Portuguese \textbullet{} Advanced\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Analysis of Algorithms
% \sectionsep
% 
% \subsection{Undergraduate}
% Artificial Intelligence \\
% {\footnotesize \textit{\textbf{(Teaching Assistant) }}} \\
% AI Robotics \\
% Operating Systems I \\
% Calculus I-IV \\
% Data Analysis I \\
% Introduction to Probability \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Societies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Societies}
% Association for Computing Machinery (ACM)\\
% Scrum Alliance Certified ScrumMaster\\
% University Honors College\\
% National Merit Scholarship Finalist \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links}
%Github:// \href{https://github.com/}{\bf JohnDoe} \\
%LinkedIn://  \href{https://www.linkedin.com/}{\bf johndoe}
%\sectionsep

\end{minipage}

\newpage

\begin{minipage}[t]{0.6\textwidth}

\runsubsection{PasswordBoss (passwordboss.com)}
\descript{| FullStack Web Developer }
\location{Jun 2021 – March 2023}
\begin{tightemize}
\item Secure data store and sharing encryption platform.
\item Full-Stack Web development with Django, NextJs and Tailwindcss.
\item Progressive web-app implemented with workbox, DexieDB and Electron.
\item REST APIs using Node.js and Django.
\item Asymetric encryption algorithms using PGP.
\item Leveraged Vue.js, Next.js and Tailwind CSS to develop dynamic and responsive user interfaces, collaborating closely with UX/UI designers.
\item CI/CD pipelines using CircleCI, Docker, and GitHub Actions.
\item Streamlining the development workflow and ensuring seamless integration of new features and bug fixing.
\item Docker containers for packaging and deploying applications to AWS infrastructure.
\item AWS services including SNS, S3, EC2, Lambda, DynamoDb
\end{tightemize}
\sectionsep

\runsubsection{Motorola R\&D (Eldorado eldorado.org.br)}
\descript{| Machine Learning Engineer }
\location{Oct 2020 – Jun 2021}
\begin{tightemize}
\item Tech lead and consultant for Motorola Camera Team.
\item Computer Vision and AI for image enhancement and reconstruction (deblurring, denoising, demosaicing, super-resolution) for Motorola phone's camera pipeline. 
\item Serverless solutions with Azure functios and Cosmos DB.
\item Edge AI for mobile phones: MLFlow, Elastic Stack, PyTorch, Keras, Tensorflow, SNPE, Jupyter, OpenCV, Pandas, Numpy, Singularity, Docker.
\end{tightemize}
\sectionsep

\runsubsection{Samsung R\&D (SIDIA sidia.com)}
\descript{| Machine Learning Engineer }
\location{Feb 2018 – Oct 2020}
\begin{tightemize}
\item Tech Lead of New Bussiness Team.
\item Practical, highly-scalable, AI \& Machine Learning pipelines for Image Classification, Face Recognition, Speech Recognition, Natural Language Processing and Reinforcement Learning.
\item Distributed architectures with Kubernetes, ZeroMQ and RabbitMQ.
\item CI/CD with Jenkins, Docker and Azure Pipelines.
\item Edge AI on Raspberry-Pi, mobile phones and web servers.
\item Development and testing of AT\&T 5G router operating system.
\item Stack: Keras, Tensorflow, Jupyter Notebooks, OpenCV, Pandas, Rasa, Spacy, Numpy, h5py.
\end{tightemize}
\sectionsep

\runsubsection{Triad Systems (itriad.org.br)}
\descript{| Full-Stack Web Developer }
\location{Jan 2016 – Feb 2018}
\begin{tightemize}
\item Analysis, development and support of ALCATEL's ERP: GlobalTools.
\item LAMP Stack Agile web development with PHP's Symfony, Django, Yii2, Angular 4, Bootstrap, Jquery, CSS3, HTML5.
\item Project lead, architect and configuration management.
\end{tightemize}
\sectionsep

 \runsubsection{UCI (uci.cu)}
 \descript{| Software Engineer }
 \location{Sept 2014 – Jan 2016}
 \begin{tightemize}
 \item Development, Test and Documentation of Cuban GNU distro: Nova.
 \item Analysis, Development and Testing of Cuban Android ROM: NovaDroid.
 \item Test Automation with Pytest. C++, Python, Linux shell scripting, Android.
 \item Development of Enterprise software solutions applied on health care used on Cuba's hospitals.
 \item Intelligent agents nets implemented with Java JADE Framework for Medical Diagnosis and Automatic Schedule Planning.
 \item Software Solutions for Medical Imaging (OpenCV, Django). 
 \item Stack: ExtJs, HTML, CSS , Symfony (PHP), Django, Java JADE, Python.
 \end{tightemize}
 
 \sectionsep

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

\section{\fontsize{12}{15}\selectfont Courses \& Certifications}

\subsection{\fontsize{10}{12}\selectfont CPA C++ Certified Associate Programmer}
\location{\fontsize{8}{10}\selectfont \href{https://verify.openedg.org}{verify.openedg.org} Code: BQ3G.bYgY.TNf5 }
\location{\fontsize{8}{10}\selectfont May 2022}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Machine Learning Engineer Nano-Degree}
\location{\fontsize{8}{10}\selectfont \href{https://confirm.udacity.com/2FCEGTAE}{confirm.udacity.com/2FCEGTAE}}
\location{\fontsize{8}{10}\selectfont Dec 2019}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Natural Language Processing (NLP) with Python NLTK}
\location{\fontsize{8}{10}\selectfont \href{https://ude.my/UC-KXA0IKSD}{ude.my/UC-KXA0IKSD}}
\location{\fontsize{8}{10}\selectfont Feb 2018}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Scrum Developer Certified}
\descript{\fontsize{8}{10}\selectfont ScrumStudy: 671161}
\location{\fontsize{8}{10}\selectfont Nov 2018}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Agile Tester (CTFL-AT)}
\descript{\fontsize{8}{10}\selectfont BSTQB: 18-CTFL-AT-08341-BR(V.2014.br)}
\location{\fontsize{8}{10}\selectfont Feb 2019}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont Certified Tester Foundation Level (CTFL)}
\descript{\fontsize{8}{10}\selectfont BSTQB: 18-CTFL-08070-BR(V.2011.br)}
\location{\fontsize{8}{10}\selectfont Nov 2018}
\sectionsep

\subsection{\fontsize{10}{12}\selectfont English as a Foreign Language Institutional Testing Program}
\descript{\fontsize{8}{10}\selectfont TOEFL: C1 527 Advanced}
\sectionsep

\section{\fontsize{12}{15}\selectfont Honors \& Awards}

\subsection{\fontsize{10}{12}\selectfont Second Best Paper}
\descript{\fontsize{8}{10}\selectfont Brasilian Symposium on Information Security}
\location{\fontsize{8}{10}\selectfont \href{https://sbseg2017.redes.unb.br/index.php/premios/}{sbseg2017.redes.unb.br/index.php/premios/}}
\location{\fontsize{8}{10}\selectfont Nov 2017}
\sectionsep


\section{\fontsize{12}{15}\selectfont Publications}

\descript{\fontsize{10}{12}\selectfont Automatic Classification of Pterygium-Non Pterygium Images Using Deep Learning}
\sectionsep

\descript{\fontsize{10}{12}\selectfont Automatic classification of light field smear microscopy patches using Convolutional Neural Networks for identifying mycobacterium tuberculosis}
\sectionsep

\descript{\fontsize{10}{12}\selectfont Improving the detection of metamorphic malware through data dependency graphs indexing}
\sectionsep

\descript{\fontsize{10}{12}\selectfont Neuro-fuzzy procedure with application in inferential sensor}
\sectionsep

\end{minipage}

\end{document}  \documentclass[]{article}
